---
title: "GCase Report"
author: "SwethaNGarimalla"
date: "3/14/2019"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::kable
```

## Objective
# Assay Introduction and Objective

Following in vivo administration of a gene therapy product, a critical assessment of the vector biodistribution is desired for target, as well as off-target, tissues. This data can be used to inform dosing and as well as tissue-specific detrimental effects and/or concerns. This assay is conducted using quantitative PCR (qPCR) to evaluate the number of vector copies per microgram of total genomic DNA in each tissue sample.

Here we report the vector copy assessment of **PR001A** for the **PRV-2018-005 non-GLP** tissue samples, including:

*	Cortex
*	Liver
*	Spleen
*	Kidney
*	Gonad
*	Heart
*	Lung

For all mice in all treatment groups.


Assay sample disposition/summary:

```{r cars}
summary(cars)
```

# Assay Test Method
* gDNA Extraction
* purelink_pro96_gdna_kit_man.pdf
* TM-001 v01 VCN by qPCR_TDF.docx
* Instrumentation
* *  Instruments used:
* * *  qPCR: QuantStudio3, serial 272321952

# Assay Results
# Discussion/Conclusions

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
